Usability of Modern Display Technologies

### 2014-10-14 mental-model-paper/paper2.tex
add first quotes for methods section

Although there exist several limitations to this study, it seems like the main limitation is the lack of tactile stuff. lack of precision can lead to more errors, but the lack of tactile response can make a system completely unusable by someone who has a visual impairment. It seems like the main concern is tactile blah. this is important because blah.

>>>>

Though literature on the subject of touchscreen display devices have presented many limitations, the most relevant and important seems to be the lack of tactile features and the requirement for heightened visual attention. For people who are blind, accessing touch screen interfaces is nearly impossible. Some accessibility features are beginning to be developed though

The principle of feedback
feedback ---sending back to the user information about what action has actually been done, what result has been accomplished--- is a well-known concept in the science of control and information theory\cite{Norman02} "In the good old days of the telephone", "telephones were designed with much more care and concern for the user. Designers at the Bell Telephone Laboratories worried a lot about feedback. The push buttons were designed to give an appropriate feel---tactile feedback. When a button was pushed, a tone was fed back into the earpiece so the user could tell that the button had been properly pushed. When the phone call was being connected, clicks, tones, and other noises gave the user feedback about the progress of the call." ``All this changed." ``Why are modern telephone systems so difficult to use? Basically, the problem is that the systems have more features and less feedback"
